---
title: "Cool and Sometimes Useful Stuff"
author: "Alia Ajina"
date: "11/30/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(usethis)
library(janitor)

# New packages
library(beepr)
library(praise)
library(cowsay)
library(paletteer)
library(sf)
```

## Beepr beeps

Use the function `beep()` in beepr package to make an audio alert when your code is done running.

** paste adds spaces default in what is returned
# EVAL = False makes it not run the entire code chunk

```{r, eval = FALSE}
for(i in rev(seq(1:99))) {
  
  print(paste(i, "bottles of beer on the wall"))
  
} 


# beep(5)
```

## praise and cowsay

packages built with a single purpose: to be kind and fun.

```{r}
praise("${Excalamtion}, ${EXCALAMATION}...${excalamtion}!!!!")



```

use_this::edit_r_profile() -> let's you change your r profile

usethis::use_git()

## paletteer to access thousands of color palettes and built in color schemes

```{r}
storms %>% 
  group_by(name) %>% 
  summarize(min_pressure = min(pressure, na.rm = TRUE)) %>% 
  slice_min(n = 10, min_pressure) %>% # top 10 lowest recorded minimum pressures
  ggplot(aes(x = min_pressure, y = name)) + 
  geom_col(aes(fill = name)) +
  scale_fill_paletteer_d("basetheme::royal") # needs to have at least 10 colors in "length"

```

## One spatial data example

```{r}
vegetation <- read_sf("doc.kml") %>% select(Name) %>% 
  clean_names()


ggplot(data = vegetation) +
  geom_sf(aes(fill = name), color = NA) + 
  theme_minimal() + 
  scale_fill_paletteer_d("ggthemes::manyeys") +
  labs(title = "Jornada Basin LTER Vegetation", 
       caption = "Source: Jornada LTER")

```

# SAVE an image file

create an image
ggsave saves the last run plot in your code as default, otherwise you can type in the name, tell it where i want to save it, could use here to point to where to save it, and what dimensions
 
```{r}
ggsave(filename = "my_awesome_map.jpg", width = 8, height = 5)
```

